### 2015-01-06 paper_10_intro.tex
new version of PDF and some minor other changes
removed Background and Overview from section 1

\subsection{BACKGROUND}

    Throughout the history of software development, many values have been 
    collected and used to measure the effectiveness of software development.

\subsection{OVERVIEW}

    What is the goal? how will it help?  Expand on the thesis statement here
    score the overall organization
    produce a single a number score
    don't focus too heavily on the source code

@@

    One area of research that is focusing on the evaluation 
    of software development organizations
    is \textit{software analytics}. 
    Software analytics is less focused on evaluation
    and more so on all sorts of analysis of software data.
    The earliest variants
    of software analytics were disguised as
    applications of data mining techniques to software 
    engineering data in the 
    late 1990s \cite{Ruhe1997,Ebert1999,Goel1997}.   
    Later the field began to emerge more heavily, but still
    remained primarily methods of data mining applied to 
    software engineering \cite{Kaner2004,Xie2009,Taylor2010,Halkidi2011}. 
    Finally, The term software intelligence was proposed for the field of study
    \cite{Hassan2010}, but eventually
    the term software analytics became the dominant term for referring to the 
    field of study \cite{Buse10, Zhang2011}.

>>>>

%\subsection{OVERVIEW}

%    Throughout the history of software development, many values have been 
%    collected and used to measure the effectiveness of software development.

%    What is the goal? how will it help?  Expand on the thesis statement here
%    score the overall organization
%    produce a single a number score
%    don't focus too heavily on the source code

@@

    One area of research that is focusing on the evaluation 
    of software development organizations
    is \textit{software analytics}. 
    Software analytics is less focused on evaluation
    and more so on all sorts of analysis of software data.
    The earliest variants
    of software analytics were disguised as
    applications of data mining techniques to software 
    engineering data in the 
    late 1990s \cite{Ruhe1997,Ebert1999,Goel1997}.   
    Later the field began to emerge more heavily, but still
    remained primarily methods of data mining applied to 
    software engineering \cite{Kaner2004,Xie2009,Taylor2010,Halkidi2011}. 
    Finally, The term software intelligence was proposed for the field of study
    \cite{Hassan2010}, but eventually
    the term software analytics became the dominant term for referring to the 
    field of study \cite{Buse2010, Zhang2011}.
